---
title: "YangZhou.1505133"
output: html_document
---


```{r set up,warning=FALSE,echo=F,message=FALSE}
library(ggplot2)
library("dplyr")  
library("RSQLite") 
library("nycflights13") 

my_db <- nycflights13_sqlite()


f1<-left_join(
  tbl(my_db, "flights"),
  tbl(my_db, "weather"),
  by = c("year","month","day","hour"))%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))

f1$month<-as.factor(f1$month)
```

#(a)Weather
###Regression
```{r regression,warning=FALSE,echo=T,eval=F,message=FALSE}
reg1<-lm(dep_delay~temp+dewp+humid+wind_dir+wind_speed++wind_gust+precip+pressure+visib,flights_weather1)
summary(reg1)

reg2<-lm(canceled~temp+dewp+humid+wind_dir+wind_speed++wind_gust+precip+pressure+visib,flights_weather1)
summary(reg2)
```
dewpoints, preciptation and wind speed has significantly increased delay, while only dewpoints has significanlty increased the probability of being canceled.

###Graph
Graph of relationship between preciptation and delayed
```{r graph,warning=FALSE,echo=T,message=FALSE}
a<-ggplot(data = sample_n(f1, 10000),aes(x=precip,y=dep_delay))
a+geom_point()+geom_line()
```

#(b)Time

```{r,echo=F,warning = F,include=F}
b1.reg<-lm(dep_delay~month+day+hour,f1)
summary(b1.reg)
b2.reg<-lm(canceled~month+day+hour,f1)
summary(b2.reg)
```

```{r, warning=F,echo=F,fig.height = 3., fig.width=6}

a.plot<-ggplot(data = sample_n(f1, 10000),aes(x=month,y=dep_delay))
a.plot+geom_point()+geom_line()

```

This plot explains the relationship between departure delays and time.



#(c)Airport Destination

```{r,warning=FALSE,message=FALSE}

dest_delay<-f1 %>%
  filter(!is.na(arr_delay)) %>%
  group_by(dest) %>%
  summarize(
    delay=mean(arr_delay),
    n=n()
  ) %>%
  arrange(-delay) 
```
The destination that has highest average delay is CAE, TUL and OKC.


#(d)characteristics 
```{r,echo=F,warning = F,include=F}
db <- nycflights13_sqlite()


d<-left_join(
  tbl(db, "flights"),
  tbl(db, "planes"),
  by = "tailnum")%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))
```

```{r,echo=F,warning = F,include=T}
d1.reg<-lm(dep_delay~engines+seats+engine,d)
d2.reg<-lm(canceled~engines+seats+engine,d)
```

```{r, warning=F,echo=F,fig.height = 3.5, fig.width=6}

a.plot<-ggplot(data = sample_n(d, 10000),aes(x=seats,y=canceled))
a.plot+geom_point()+geom_line()
```

number of seats and engines are statistically significant in determining cancelled flights. Other characteristics are not.






